\thetitle

### 2021-03-01 writing/mutate-mutators.tex
adjust prose

Figure~\ref{table:mutation-ops} describes 16 mutators that satisfy this
requirement.  For each mutator, the figure provides a short description and an
example. The starting point is the mutator set of~\citet{lksfd-popl-2020}
which in turn are borrowed from the vast literature on mutation
testing~\cite{jia2011analysis}. But, only 2 of the previous mutators transfer
as is to the context of this study, 1 is entirely ineffective and 5 need
significant modifications. For the latter the authors relied on their
decades-long experience of making type-level mistakes in Typed Racket, some of
which take a non-trivial effort to debug.  In more detail, the relational
mutator of ~\citet{lksfd-popl-2020} does not lead to type-level errors that
Typed Racket's type system can detect, so it has been eliminated. Similarly,
the original arithmetic mutator does not reliably lead to type errors, so it
has been adapted to only make operator swaps that can affect the type of the
result. For example, changing a `/` to `*` does not affect the type of an
expression, but changing `*` to `/` may s division by zero is detectable by
Typed Racket's type system.  In addition to careful tweaking of previous
mutators, the final set of mutators comes with 9 new ones that collectively
produce a sufficiently large and diverse set of type-level mistakes.  For
example, unlike the traditional subexpression swap mutator, the {\tt -id}
family of mutators apply in different contexts and utilize different pieces of
non-local information about the identifiers in a program.

>>>>

Figure~\ref{table:mutation-ops} describes 16 mutators that satisfy this
requirement.  For each mutator, the figure provides a short description and an
example. As the explanation indicates, some specialize or
generalize~\citet{lksfd-popl-2020}'s mutators, which in turn are borrowed from
the vast literature on mutation testing~\cite{jia2011analysis}.\footnote{Many
of~\citet{lksfd-popl-2020} mutators do not satisfy the constraints. For
example, the relational mutator does not lead to type-level errors that Typed
Racket's type system can detect, so it has been eliminated. Similarly, the
original arithmetic mutator does not reliably lead to type errors, so it has
been adapted to only make operator swaps that can affect the type of the
result. Changing a `/` to `*` does not affect the type of an expression, but
changing `*` to `/` may, because division by zero is detectable by Typed
Racket's type system.}  Only two are directly inherited; many mutators are
brand new. For the latter the authors relied on their decades-long experience
of making type-level mistakes in Typed Racket, some of which take a non-trivial
effort to debug.
